\documentclass[a4paper,11pt]{letter}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry} % To adjust margins
\usepackage{parskip} % To avoid indentation in paragraphs

\geometry{top=1in, bottom=1in, left=1in, right=1in}

% Hyperref package with custom link color for email
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref} % Blue colored clickable links

\signature{Md. Akhtarul Islam Boshunia Rahat} % Signature
\address{Kadritech AB \\ Backend Developer\\ 
\href{mailto:rahatakhter4@gmail.com}{\underline{rahatakhter4@gmail.com}}\\ 
+8801955-021432} % Your address

% Manually set the date with GMT+6 timezone in mind
\date{currentDate} % Adjusted date



\begin{document}

\begin{letter}{Hiring Manager \\ companyName}

\opening
{Dear Hiring Manager}

I am writing to express my interest in the appliedPosition position at companyName. With a solid background in competitive programming and a Bachelor’s degree in Mechanical Engineering from Khulna University of Engineering \& Technology (KUET), I believe my technical skills and problem-solving abilities would be a valuable addition to your team.

Currently, I am employed as a Backend Developer at Kadritech AB, where I primarily work with Node.js. My job involves fixing bugs, developing new features, and improving API performance to ensure our software is efficient and scalable. Recently, I implemented a feature that allows shop owners to upload bulk products using an Excel file, and I used MongoDB aggregation queries to handle complex data needs. My experience in competitive programming has helped me to think analytically, which I use to tackle challenges, such as improving execution times by replacing traditional database queries inside for-of loops with Promise.all, taking advantage of javascript's asynchronous nature. This journey has greatly contributed to my growth as a programmer and has enhanced my understanding of how to create reliable and effective software. Besides, I work in Ubuntu and am familiar with common terminal commands.

My skills in data structures and algorithms have grown through extensive participation in various competitive programming contests. I’ve had the privilege to compete in well-known events such as the ACM ICPC Dhaka Regional 2020 and the NSU Cybernauts National Programming Contest 2019, where I gained valuable experience and performed well. Additionally, I achieved high rankings in the KU CSE Fest 2022 and the Red.Digital Digi-Thor Programming Contest 2020, which helped further develop my problem-solving abilities.


I am excited about the opportunity to bring my skills in software development, attention to detail, and passion for problem-solving to your company. I have attached my resume for your consideration and would welcome the chance to discuss how my background aligns with your team’s needs.

Thank you for your time and consideration. I look forward to the possibility of contributing to your team.\\

Best Regards\\
Md. Akhtarul Islam Boshunia Rahat

\end{letter}

\end{document}



